Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

[ESTC-analyses](https://github.com/rOpenGov/estc)
([LIBER](https://github.com/rOpenGov/estc/blob/master/inst/examples/20151023-LIBER.md)
in particular); toisto Fennica/Kungliga datoilla ? LL: Voidaan tehda
mut kandee miettia ehka spesifimmin et mitka analyysit sielta
kiinnostaa. Muuten menee aikaa hukkaan jos pitaa fiksata juttuja joita
ei sitten kaytetakaan.

@@

```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=10}
theme_set(theme_bw(20))
dfs <- fen %>% filter(author_gender == "female")
p <- top_plot(dfs, "author", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count")
p <- p + ggtitle("Top female authors (Fennica)")
p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
pf = p

@@

```{r LIBER-topplace, echo=FALSE, message=FALSE, cache=FALSE, fig.height=6, fig.width=6}
theme_set(theme_bw(30))
p <- top_plot(fen, "publication_place", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count (Log10 scale)")
p <- p + scale_y_log10()
p <- p + ggtitle("Top publication places (Fennica)")
pf = p

theme_set(theme_bw(30))
p <- top_plot(kun, "publication_place", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count (Log10 scale)")
p <- p + scale_y_log10()
p <- p + ggtitle("Top publication places (Kungliga)")
pk = p

@@

Paper consumption for different document formats over time. Each point represents a decade. Loess smoothing. Fennica.

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6}
df2 <- df %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
p <- p + geom_point(size = 4)
p <- p + geom_smooth(method = "loess", size = 1, color = "black")
p <- p + ggtitle("Paper consumption in time by gatherings")
p <- p + xlab("Year")
p <- p + ylab("Paper consumption (km2)")
p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
p <- p + ggtitle("Paper consumption for different document formats")
print(p)
```

@@

## Miscellaneous figures to consider

>>>>

@@

```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=15, out.width="850px"}
theme_set(theme_bw(10))
dfs <- fen %>% filter(author_gender == "female")
p <- top_plot(dfs, "author", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count")
p <- p + ggtitle("Top female authors (Fennica)")
p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
pf = p

@@

```{r LIBER-topplace, echo=FALSE, message=FALSE, cache=FALSE, fig.height=6, fig.width=12}
theme_set(theme_bw(20))
ntop = 10
p <- top_plot(fen, "publication_place", ntop = ntop)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count (Log10 scale)")
p <- p + scale_y_log10()
p <- p + ggtitle("Top publication places\n(Fennica)")
pf = p

theme_set(theme_bw(30))
p <- top_plot(kun, "publication_place", ntop = ntop)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count (Log10 scale)")
p <- p + scale_y_log10()
p <- p + ggtitle("Top publication places\n(Kungliga)")
pk = p

@@

Paper consumption for different document formats over time. Each point represents a decade. Loess smoothing.

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="430px"}
for (catal in unique(df0$catalogue)) {
  df2 <- subset(df0, catalogue == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper consumption (km2)")
  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
  print(p)
}

```

@@

## Miscellaneous ideas to consider

[ESTC-analyses](https://github.com/rOpenGov/estc)
([LIBER](https://github.com/rOpenGov/estc/blob/master/inst/examples/20151023-LIBER.md)
in particular); toisto Fennica/Kungliga datoilla ? LL: lisäilin
joitain analyyseja tahan mutta jos tahdotte lisaa niin pyytakaa
erikseen.
